Review of Assigned Readings

### 2017-12-28 documentation/documentation.tex
add requirement.txt and add setup part to documentation

@@

\subsubsection{Process}
The process of the script \verb|aggregateTwitterBpi.py| works as follows:
\begin{figure}[H]
    \centering
    \begin{tikzpicture}[node distance=1.6cm]
        \node (start) [startstop] {Start};
        \node (pro1) [process, below of=start] {Load BPI data set};
        \node (pro2) [process, below of=pro1] {Calculate first differences for BPI data};
        \node (pro3) [process, below of=pro2] {Load tweets data set};
        \node (pro4) [process, below of=pro3] {Count number of tweets on an hourly basis};
        \node (pro5) [process, below of=pro4] {Calculate first differences for number of tweets on an hourly basis};
        \node (pro6) [process, below of=pro5] {Merge number of tweets with BPI data (incl. first differences)};
        \node (pro7) [process, below of=pro6] {Generate and save CSV file};
        \node (stop) [startstop, below of=pro7] {Stop};

@@

Here a short description of what happens at the various steps: 
\linebreak\linebreak
\textbf{Load BPI data set} The script takes the BPI data set that is located at \verb|data/bpi.csv|.
\linebreak\linebreak
\textbf{Calculate first differences for BPI data} The first differences of the BPI closing prices and the natural logarithm of the first differences of the BPI closing prices are calculated. The reason for calculating these values is given in the data analysis section.
\linebreak\linebreak
\textbf{Load tweets data set} The script takes the tweets data set that is located at \verb|data/twitterData.csv|.
\linebreak\linebreak
\textbf{Count number of tweets on an hourly basis} 
\linebreak\linebreak
\textbf{Calculate first differences for number of tweets on an hourly basis} 
\linebreak\linebreak
\textbf{Merge number of tweets with BPI data (incl. first differences)} 
\linebreak\linebreak
\textbf{Generate and save CSV file}

\subsubsection{Execution}
By executing the Python script \verb|aggregateTwitterBpi.py| a aggregated data set that contains number of tweets and Bitcoin Price Index, both on an hourly basis, gets generated. 
\begin{lstlisting}[language=bash]
    $ python aggregateTwitterBpi.py
\end{lstlisting}

\subsubsection{Output}
After successfully running the Python script \verb|aggregateTwitterBpi.py| the file \verb|nr_of_tweets_bpi_closing_price.csv| is generated in the folder \verb|/data|. It is important to note that every execution of the script overwrites any existing \verb|nr_of_tweets_bpi_closing_price.csv| file.

>>>>

\section{Setup}
\subsection{Requirements to run Python scripts}
Before you go any further, make sure that at least Python version 3.0.0 available from your command line. You can check this by running:
\begin{lstlisting}[language=bash]
    python --version
\end{lstlisting}
You should get some output like Python 3.7.13. If you do not have at least Python version 3.0.0, please install the latest 3.x version from python.org.
\newline
On top you need various packages. We created a the requirements file \verb|requirements.txt|, which contains all required packages to run Python scripts of the project. The list of packages to be installed using pip install like so:
\begin{lstlisting}[language=bash]
    pip install -r requirements.txt
\end{lstlisting}
Now you should be ready to run the Python scripts.

\subsection{Stata}
(Dimitri's Part: stata version and anything else required to do your calculations)

@@

\subsection{Process}
The process of the script \verb|aggregateTwitterBpi.py| works as follows:
\begin{figure}[H]
    \centering
    \begin{tikzpicture}[node distance=1.6cm]
        \node (start) [startstop] {Start};
        \node (pro1) [process, below of=start] {Load BPI data set};
        \node (pro2) [process, below of=pro1] {Calculate first differences for BPI data};
        \node (pro3) [process, below of=pro2] {Load tweets data set};
        \node (pro4) [process, below of=pro3] {Count number of tweets on an hourly basis};
        \node (pro5) [process, below of=pro4] {Calculate first differences for number of tweets on an hourly basis};
        \node (pro6) [process, below of=pro5] {Merge number of tweets with BPI data (incl. first differences)};
        \node (pro7) [process, below of=pro6] {Generate and save CSV file};
        \node (stop) [startstop, below of=pro7] {Stop};

@@

Here a short description of what happens at the various steps: 
\linebreak\linebreak
\textbf{Load BPI data set} The script takes the BPI data set that is located at \verb|data/bpi.csv|.
\linebreak\linebreak
\textbf{Calculate first differences for BPI data} The first differences of the BPI closing prices and the natural logarithm of the first differences of the BPI closing prices are calculated. The reason for calculating these values is given in the data analysis section.
\linebreak\linebreak
\textbf{Load tweets data set} The script takes the tweets data set that is located at \verb|data/twitterData.csv|.
\linebreak\linebreak
\textbf{Count number of tweets on an hourly basis} First, groups the tweets by hour. Second, counts the number of tweets for every hour.
\linebreak\linebreak
\textbf{Calculate first differences for number of tweets on an hourly basis} The first differences of the number of tweets and the natural logarithm of the first differences of the number of tweets are calculated. Again, the reason for calculating these values is given in the data analysis section.
\linebreak\linebreak
\textbf{Merge number of tweets with BPI data (incl. first differences)} 
Insert Image
\linebreak\linebreak
\textbf{Generate and save CSV file} Finally, a CSV file is generated with the merged data.

\subsection{Execution}
By executing the Python script \verb|aggregateTwitterBpi.py| a aggregated data set that contains number of tweets and Bitcoin Price Index, both on an hourly basis, gets generated. 
\begin{lstlisting}[language=bash]
    $ python aggregateTwitterBpi.py
\end{lstlisting}

\subsection{Output}
After successfully running the Python script \verb|aggregateTwitterBpi.py| the file \verb|nr_of_tweets_bpi_closing_price.csv| is generated in the folder \verb|/data|. It is important to note that every execution of the script overwrites any existing \verb|nr_of_tweets_bpi_closing_price.csv| file.
